Understanding domestic abuse - Pathways to Impact

### 2019-07-30 pathways_to_impact.tex
Anna update

In addition to working with WMP, our links to the National Police Chiefs council, and collaboration with the CoP, provide pathways for impact across all forces. At the CoP (situated just a few miles from Warwick campus) we will work within the framework of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/)}{Authorised Professional Practice} released in 2015. Insights from our work on the predictors of serious harm will contribute to the \href{https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{revision of the existing DASH risk assessment tool} for domestic abuse. \citeNP{dash} have shown that the DASH framework has poor predictive performance, as only 4 out of 25 risk factors were associated with an increased risk of repeat perpetration. We will work initially with David Tucker, Head Crime and Criminal Justice at the CoP.

>>>>

In addition to working with WMP, our links to the National Police Chiefs council, and collaboration with the CoP, provide pathways for impact across all forces. Our work will contribute to the ongoing refinement of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/)}{Authorised Professional Practice} framework in the context of domestic abuse. This framework is the primary guidance for police response strategy, there this refinement will result in real change in policing practices and improve victims' experiences. Insights from our work on the predictors of serious harm will contribute to the \href{https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{revision of the existing DASH risk assessment tool} for domestic abuse. \citeNP{dash} have shown that the DASH framework has poor predictive performance, as only 4 out of 25 risk factors were associated with an increased risk of repeat perpetration. We will work initially with David Tucker, Head Crime and Criminal Justice at the CoP.
